### 2017-08-22 paper/incomeShocks-jde-r1.tex
Add age group results to appendix
Add effects on different contraceptive to appendix

% Age groups and crop loss effects
\caption{The Effects of Crop Loss by Age}
\label{tab:agegroups}
\begin{tabular}{@{} l D{.}{.}{2.6} D{.}{.}{2.6}  D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6}  @{}}
Crop loss - 1-7 months \X age 18-22                    &      -0.160\sym{**} &                     &       0.096\sym{*}  &       0.048         &      -0.003         \\
                                                       &     (0.075)         &                     &     (0.052)         &     (0.044)         &     (0.016)         \\
Crop loss - 1-7 months \X age 23-27                    &      -0.170\sym{**} &                     &       0.004         &      -0.017         &       0.009         \\
                                                       &     (0.072)         &                     &     (0.066)         &     (0.063)         &     (0.019)         \\
Crop loss - 1-7 months \X age 28-32                    &      -0.153\sym{**} &                     &       0.149\sym{**} &       0.126\sym{**} &       0.029         \\
                                                       &     (0.065)         &                     &     (0.058)         &     (0.055)         &     (0.031)         \\
Crop loss - 1-7 months \X age 33-37                    &       0.031         &                     &       0.048         &       0.038         &       0.001         \\
                                                       &     (0.072)         &                     &     (0.070)         &     (0.055)         &     (0.044)         \\
Crop loss - 1-7 months \X age 38-45                    &      -0.021         &                     &       0.020         &       0.050         &      -0.034\sym{*}  \\
                                                       &     (0.043)         &                     &     (0.054)         &     (0.048)         &     (0.020)         \\
Crop loss - 7-14 months \X age 18-22                   &                     &      -0.235\sym{***}&                     &                     &                     \\
                                                       &                     &     (0.087)         &                     &                     &                     \\
Crop loss - 7-14 months \X age 23-27                   &                     &      -0.129         &                     &                     &                     \\
                                                       &                     &     (0.094)         &                     &                     &                     \\
Crop loss - 7-14 months \X age 28-32                   &                     &      -0.225\sym{***}&                     &                     &                     \\
                                                       &                     &     (0.073)         &                     &                     &                     \\
Crop loss - 7-14 months \X age 33-37                   &                     &      -0.127         &                     &                     &                     \\
                                                       &                     &     (0.082)         &                     &                     &                     \\
Crop loss - 7-14 months \X age 38-45                   &                     &      -0.042         &                     &                     &                     \\
                                                       &                     &     (0.050)         &                     &                     &                     \\
Age groups is based on age at the first round of the survey as described in the text.

@@

% Excluding abstinence

\begin{table}[htbp]
\begin{center}
\begin{small}
\begin{threeparttable}
\caption{Crop loss and Abstinence as Contraceptives}
\label{tab:excludeAbs}
\begin{tabular}{@{} l D{.}{.}{2.6} D{.}{.}{2.6}  D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6}   @{}}
\toprule
                                                       & \multicolumn{4}{c}{Contraceptive Use}\\ \cmidrule(lr){2-5}
                                                       & \mct{Any, except abstinence}              & \mct{Rhythm and withdrawal}               & \mct{Only abstinence}                     \\ \midrule
Crop loss - 1-7 months                                 &       0.036         &       0.039         &       0.018         &       0.002         &       0.021         &       0.025         \\
\hs (200 TZS or above)                                 &     (0.030)         &     (0.031)         &     (0.021)         &     (0.026)         &     (0.019)         &     (0.027)         \\
Crop loss - 1-7 months                                 &                     &      -0.000         &                     &       0.002         &                     &      -0.000         \\
\hs  \X initial assets (10,000 TZS)                    &                     &     (0.003)         &                     &     (0.002)         &                     &     (0.003)         \\
\addlinespace 
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Observations                                           &    \mco{988}        &    \mco{988}        &    \mco{988}        &    \mco{988}        &    \mco{988}        &    \mco{988}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
Assets are per capita and measured in 10,000 TZS.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{center}
\end{table}

>>>>

% Age groups and crop loss effects
\input{../tables/appendix_age_groups.tex}

@@

% Excluding abstinence
\input{../tables/appendix_exclude_abstinence.tex}
